Elite orientation of an education system and economic growth

### 2024-04-26 paper/main.tex
latest

The allocation of the talented people in a country may provide important economic effects when they work in value-generating positions (i.e. entrepreneurship) versus rent-seeking ones (Murphy et. al., 1991). Within specific industries, the development of technology has allowed superstars to dominate financially at the expense of more moderate performers (Rosen 1981). There are clear economic effects from talented individuals at a country and the same technology which made superstars rich may do the same for countries as well.

@@

\section{Data}
To investigate the central question of the relationship between elite academic performance and GDP per capita growth, I combined national-level data through 2003-2022 from World Bank: World Development Indicators, the Academic Ranking of World Universities (ARWU), PISA test data, the Economist Intelligence Unit Democracy Index, and International Math Olympiad performance results.

>>>>

The allocation of the talented people in a country may provide important economic effects when they work in value-generating positions (i.e. entrepreneurship) versus rent-seeking ones (Murphy et. al., 1991). Within specific industries, the development of technology has allowed superstars to dominate financially at the expense of more moderate performers (Rosen 1981). There are clear economic effects from talented individuals in a country. The same technology which made individual superstars rich may do the same for countries as well which produce and use their superstars well.

@@

\section{Data}
To investigate the central question of the relationship between elite academic performance and GDP per capita growth, I combined national-level data through 2003-2022 from World Bank: World Development Indicators, the Academic Ranking of World Universities (ARWU), PISA test data, the Economist Intelligence Unit Democracy Index, and International Math Olympiad performance results. \footnote{The definition of a ``country'' can be controversial. This paper considers a country to be the ones intersecting with the World Bank, the IMO, and ARWU. Not all of these are UN-recognized}
